---
title: "P8105_HW6-yz4188"
author: "Yueran Zhang"
date: "12/02/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
```

#Problem 1 
```{r}
birthweight_df = read_csv("./birthweight.csv")
```


```{r}
## checking miss value
skimr::skim(birthweight_df)$n_missing 
```
There is no missing value in our dataframe.



```{r}
## convert variables into factor
birthweight_df =
  birthweight_df %>%
    mutate(babysex = recode_factor(babysex, "1" = "male", "2" = "female")) %>% 
    mutate(frace = recode_factor(frace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other", "9" = "Unknown")) %>% 
    mutate(malform = recode_factor(malform, "0" = "absent", "1" = "present")) %>% 
    mutate(mrace = recode_factor(mrace, "1" = "White", "2" = "Black", "3" = "Asian", "4" = "Puerto Rican", "8" = "Other")) 

birthweight_df
```

```{r}
## propose a regression model for birthweight
fit = lm(bwt ~ wtgain * ppwt, data = birthweight_df)
  
fit %>% 
   broom::tidy() %>% 
   select(term, estimate, p.value) %>%
   knitr::kable(digits = 3)

birthweight_df %>% 
  modelr::add_predictions(fit) %>%
  modelr::add_residuals(fit) %>%
  ggplot(aes(x = pred,y = resid)) + geom_violin() 

```


```{r}
## compare with two other models
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    fit = map(train, ~ lm(bwt~ wtgain * ppwt, data =.x )),
    model_1 = map(train, ~ lm(bwt ~ blength + gaweeks, data =.x )),
    model_2 = map(train, ~ lm(bwt ~ bhead * blength * babysex, data =.x ))) %>%
  
  mutate(
    rmse_fit = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))

cv_plot =  cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()

cv_plot

```

From our plot, we can know that`model_2` is the best model to describe, which used head circumference, length, sex and all interactions.


#Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
## bootsample and check for it 
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}

boot_sample(weather_df) %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")

```


## Bootstrap

### R_Square
```{r, echo=FALSE}
set.seed(1)

R_square = 
    tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
```

```{r}
R_square_results =
  R_square %>%
mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    r_results = map(models, broom::glance)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(r_results) 

R_square_results
```

```{r}
R_square_results %>%
  ggplot(aes(x = r.squared)) +
  geom_density()
```

```{r}
R_square_results %>% 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))

```
For the R_square is a left skewed distribution. The mean value is  `r mean(pull(R_square_results,r.squared))`; the median value is `r median(pull(R_square_results,r.squared))`; the standard deviation is `r sd(pull(R_square_results,r.squared))`; the lower of 95% CI  is `r quantile(pull(R_square_results,r.squared), 0.025)`, the upper of 95% CI is 
`r quantile(pull(R_square_results,r.squared), 0.975)`.


### log_Beta
```{r}
set.seed(1)

Beta_df = 
    tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather_df))
  )
```

```{r}
Beta_results =
  Beta_df %>%
mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x) ),
    beta_results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(beta_results) 

Beta_results
```


```{r}
log_beta = 
  Beta_results %>%
  select(strap_number, term, estimate) %>%
  pivot_wider(names_from = term,values_from = estimate) %>%
  mutate(logbeta = log(`(Intercept)`*tmin))
  
```

```{r}
log_beta %>%
  ggplot(aes(x = logbeta)) +
  geom_density()
```

For the log_beta  is a normal distribution. The mean value is  `r mean(pull(log_beta,logbeta))`; the median value is `r median(pull(log_beta,logbeta))`; the standard deviation is `r sd(pull(log_beta,logbeta))`; the lower of 95% CI  is `r quantile(pull(log_beta,logbeta), 0.025)`, the upper of 95% CI is `r quantile(pull(log_beta,logbeta), 0.975)`.

